### 2022-12-05 ms.rmd
Added scale cv and acf to data and models

###################################################
  # Model 3.2: Model controlling for acclimation time, 
  # type and habitat assuming type can vary by habitat
###################################################
rerun = TRUE
if(rerun){
  # More realistic model with 
  model3.2          <- metafor::rma.mv(effect_size ~ c_accl_time + type + habitat + type:habitat, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild)

@@

####################################################
  # Model 3.3: Model environmental variability by acute 
  #  acclim 
####################################################
  rerun = TRUE
if(rerun){
  # More realistic model with 
  model3.3          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(cv) + type + type:scale(cv), V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild)

   model3.3_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(cv) + type + type:scale(cv) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)

@@

################################################################
  # Model 3.7: Environmental autocorrelation model by acute/acclim
################################################################
  if(rerun){
  # More realistic model with 
  model3.4          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(acf_all) + type + type:scale(acf_all), V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild)

   model3.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(acf_all) + type + type:scale(acf_all) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)

@@

################################################################
  # Model 3.5: Environmental variability  model
################################################################
  if(rerun){
  # More realistic model with 
  model3.5          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(cv) + type, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild)

   model3.5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(cv) + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)

@@

################################################################
  # Model 3.6: Environmental autocorrelation model
################################################################
  if(rerun){
  # More realistic model with 
  model3.6          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(acf_all) + type, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild)

   model3.6_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(acf_all) + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)

@@

  if(rerun){
  # More realistic model with 
  model3.7          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(acf_all) + scale(cv) + type, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild)

   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(acf_all) + scale(cv) + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)

@@

###################################################
  # Model 4.2: Model controlling for acclimation time, 
  # type and habitat assuming type can vary by habitat
###################################################
rerun = FALSE
if(rerun){
  # More realistic model with 
  model4.2          <- metafor::rma.mv(effect_size ~ c_accl_time + type + habitat + type:habitat, V = V,
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data_wild)

@@

####################################################
  # Model 4.3: Model environmental variability by acute/acclim
####################################################
  rerun = FALSE
if(rerun){
  # More realistic model with 
  model4.3          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(cv) + type + type:scale(cv), V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data_wild)

   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(cv) + type + type:scale(cv) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)

@@

################################################################
  # Model 4.4: Environmental autocorrelation model by acute/acclim
################################################################
  if(rerun){
  # More realistic model with 
  model4.4          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(acf_all) + type + type:scale(acf_all), V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data_wild)

   model4.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(acf_all) + type + type:scale(acf_all) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)

@@

################################################################
  # Model 4.5: Environmental variability
################################################################
if(rerun){
  # More realistic model with 
  model4.5          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(cv) + type, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data_wild)

   model4.5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(cv) + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)

@@

################################################################
  # Model 4.6: Environmental autocorrelation model 
################################################################
  if(rerun){
  # More realistic model with 
  model4.6          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(acf_all) + type, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data_wild)

   model4.6_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(acf_all) + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)

@@

################################################################
  # Model 4.7: Environmental autocorrelation and variability
################################################################
 if(rerun){
  # More realistic model with 
  model4.7          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(acf_all) + scale(cv) + type, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data_wild)

   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(acf_all) + scale(cv) + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)

@@

>>>>

# Scale data
        lnRRQ10_data_wild <- lnRRQ10_data_wild %>% mutate(cv_c = scale(cv),
                                                          acf_all_c = scale(acf_all))
###################################################
  # Model 3.2: Model controlling for acclimation time, 
  # type and habitat assuming type can vary by habitat
###################################################
rerun = TRUE
if(rerun){
  # More realistic model with 
  model3.2          <- metafor::rma.mv(effect_size ~ c_accl_time + type + habitat + type:habitat, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild)

@@

####################################################
  # Model 3.3: Model environmental variability by acute 
  #  acclim 
####################################################
  rerun = TRUE
if(rerun){
  # More realistic model with 
  model3.3          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type + type:cv_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild)

   model3.3_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)

@@

################################################################
  # Model 3.7: Environmental autocorrelation model by acute/acclim
################################################################
  if(rerun){
  # More realistic model with 
  model3.4          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type + type:acf_all_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild)

   model3.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)

@@

################################################################
  # Model 3.5: Environmental variability  model
################################################################
  if(rerun){
  # More realistic model with 
  model3.5          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild)

   model3.5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)

@@

################################################################
  # Model 3.6: Environmental autocorrelation model
################################################################

  if(rerun){
  # More realistic model with 
  model3.6          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild)

   model3.6_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)

@@

  if(rerun){
  # More realistic model with 
  model3.7          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + cv_c + type, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild)

   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)

@@

# Scale environment variables
    lnCVRQ10_data_wild <- lnCVRQ10_data_wild %>% mutate(     cv_c = scale(cv),
                                                        acf_all_c = scale(acf_all))
###################################################
  # Model 4.2: Model controlling for acclimation time, 
  # type and habitat assuming type can vary by habitat
###################################################
rerun = FALSE
if(rerun){
  # More realistic model with 
  model4.2          <- metafor::rma.mv(effect_size ~ c_accl_time + type + habitat + type:habitat, V = V,
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data_wild)

@@

####################################################
  # Model 4.3: Model environmental variability by acute/acclim
####################################################
  rerun = FALSE
if(rerun){
  # More realistic model with 
  model4.3          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type + type:cv_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data_wild)

   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)

@@

################################################################
  # Model 4.4: Environmental autocorrelation model by acute/acclim
################################################################
  if(rerun){
  # More realistic model with 
  model4.4          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type + type:acf_all_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data_wild)

   model4.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)

@@

################################################################
  # Model 4.5: Environmental variability
################################################################
if(rerun){
  # More realistic model with 
  model4.5          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data_wild)

   model4.5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)

@@

################################################################
  # Model 4.6: Environmental autocorrelation model 
################################################################
  if(rerun){
  # More realistic model with 
  model4.6          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data_wild)

   model4.6_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)

@@

################################################################
  # Model 4.7: Environmental autocorrelation and variability
################################################################
 if(rerun){
  # More realistic model with 
  model4.7          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + cv_c + type, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data_wild)

   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)

@@

```{r, fig6, fig.align='center', fig.cap= "I2 estimates lnCVR"}
p6 <- bubble_plot(model3.5, mod = "cv", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)")

p7 <- bubble_plot(model3.6, mod = "acf_all", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Autocorrelation") + theme(axis.title.y = element_blank())

p67 <- (p6 | p7) + plot_annotation(tag_levels = "A")

ggsave(p67, filename = "./output/figures/fig6.png")
```
